\documentclass[twocolumn]{IEEEtran}

\usepackage{macros}
\pdfminorversion=4

% The following packages will be automatically loaded:
% amsmath, amssymb, natbib, graphicx, url, algorithm2e
\begin{document}

\title{Stochastic optimization in a cumulative prospect theory framework$^\star$\thanks{$\star$ Supported by NSF under Grants CMMI-1434419, CNS-1446665, and
CMMI-1362303, by AFOSR under Grant FA9550-15-10050 and the Alberta Innovates Technology Futures through the Alberta Ingenuity Centre for Machine Learning, NSERC.}}
\author{Cheng Jie$^\sharp$, Prashanth L.A.$^\dagger$, Michael Fu$^\$$, Steve Marcus$^\ddag$ and Csaba Szepesv\'ari$^\natural$
\thanks{
$\sharp$ Department of Mathematics,
University of Maryland, College Park, Maryland, 
E-Mail: cjie@math.umd.edu, 

$^\dagger$ Institute for Systems Research, University of Maryland, College Park, Maryland,
E-Mail: prashla@isr.umd.edu,

$\$$ Robert H. Smith School of Business \& Institute for Systems Research,
University of Maryland, College Park, Maryland,
E-Mail: mfu@isr.umd.edu,

$\ddag$ Department of Electrical and Computer Engineering \& Institute for Systems Research,
University of Maryland, College Park, Maryland,
 E-Mail: marcus@umd.edu.

$\natural$ Department of Computing Science,
University of Alberta,
 E-Mail: szepesva@cs.ualberta.ca.
}}
\maketitle


\begin{abstract}
%aa
%In several real-world systems involving humans, traditional expected value cannot explain the observed behavior and incorporating distortions in the underlying probabilities of the system can alleviate this problem. 
Cumulative prospect theory (CPT) is a very popular approach that is based on probabilistic distortions and is more general than the expected value.  We bring this idea to a stochastic optimization framework and propose algorithms for both estimation and optimization of the CPT-value objective. We propose an empirical distribution function based scheme to estimate the CPT-value and then use this scheme in the inner loop of a CPT-value optimization procedure. We propose both gradient-based as well as gradient-free CPT-value optimization algorithms, that are based on two well-known simulation optimization ideas: simultaneous perturbation stochastic approximation (SPSA) and model-based parameter search (MPS), respectively.  We provide theoretical convergence guarantees for all the proposed algorithms 
and also illustrate the usefulness of CPT-based criteria in a traffic signal control application.
\end{abstract}

% You may provide any keywords that you 
% find helpful for describing your paper; 
\begin{IEEEkeywords}
Cumulative prospect theory, stochastic optimization, simultaneous perturbation stochastic approximation, reinforcement learning.
\end{IEEEkeywords}

\section{Introduction}
\label{sec:introduction}

\input{intro}

%%%%%%%%%%%%%5
\section{CPT-value}
\label{sec:cpt-val}
\input{cptval}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{CPT-value estimation} 
\label{sec:cpt-sampling}

\input{estimation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CPT-value optimization}
\label{sec:cpt-control}
\input{algos}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Convergence Proofs}
\label{sec:convergence}
\input{conv-proofs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Experiments}
\label{sec:expts}

\input{simple-expts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Traffic Control Application}
\label{sec:expts}

\input{experiments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Conclusions}
\label{sec:conclusions}
CPT has been a very popular paradigm for modeling human decisions among psychologists/economists and this work is the first step in incorporating CPT-based criteria into a stochastic optimization framework. Estimation and optimization of CPT-based value is challenging. 
%Using temporal-difference learning type algorithms for estimation was ruled out for CPT-value since the underlying probabilities get (non-linearly) distorted by a weight function. 
For estimating the CPT-value, we proposed a quantile-based estimation scheme and for maximizing the CPT-value, we adapted SPSA \cite{spall} and MPS \cite{chang2013simulation} algorithms. 
We provided theoretical convergence guarantees for all the proposed algorithms and illustrated the usefulness of our algorithms for optimizing CPT-based criteria in a traffic signal control application.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\subsubsection*{Acknowledgments}
%This work was supported by the Alberta Innovates Technology Futures through the Alberta Ingenuity Centre for Machine Learning, NSERC, the National Science Foundation (NSF) under Grants CMMI-1434419, CNS-1446665, and CMMI-1362303, and by the Air Force Office of Scientific Research (AFOSR) under Grant FA9550-15-10050.
%
%\clearpage
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
\bibliography{cpt-refs}

 %\section*{Appendix}

%\input{appendix}
\end{document}


